---
title: "Seurat Integration and Cluster Assignment for Midbrain Pilot 2 and MTG Batch 7 and 8"
output: html_document
---

```{R}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
library(SeuratWrappers)
library(glmpca)
library(stringr)
```





```{r}
Batch8.data <- Read10X(data.dir = "~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch27_ASAP_snRNA-seq_120721/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
Batch7.data <- Read10X(data.dir = "~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch28_ASAP_snRNA-seq_120821/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
Batch9.data <- Read10X(data.dir = "~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch29_ASAP_snRNA-seq_121021/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
Batch10.data <- Read10X(data.dir = "~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch30_ASAP_snRNA-seq_121421/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
```

batch9_ASAP_snRNA-seq_062221
batch10_ASAP_snRNA-seq_062321

```{R}
Batch7samples <- read.csv(file.path("~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch27_ASAP_snRNA-seq_120721/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)
Batch8samples <- read.csv(file.path("~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch28_ASAP_snRNA-seq_120821/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)
Batch9samples <- read.csv(file.path("~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch29_ASAP_snRNA-seq_121021/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)
Batch10samples <- read.csv(file.path("~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/batch30_ASAP_snRNA-seq_121421/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)

```


```{R}
Batches <- ls()[grep("[[:digit:]].data",ls())]

createmetadata <- function(batch) {
  batchdf <- get(batch)
  tempcellcodes <- as.data.frame(batchdf@Dimnames[[2]])
  colnames(tempcellcodes) <- "barcodes"
  tempcellcodes$libcodes <- as.factor(gsub(pattern=".+-", replacement="", tempcellcodes$barcodes))
  prefix <- str_extract(batch,"Pilot_|Batch")
  samptable <- paste(prefix,str_extract(batch,"[[:digit:]]+"),"samples",sep="")
  tempcellcodes$samples <- as.vector(get(paste(prefix,str_extract(batch,"[[:digit:]]+"),"samples",sep=""))$library_id[tempcellcodes$libcodes])
  tempcellcodes$case <- as.vector(get(paste(prefix,str_extract(batch,"[[:digit:]]+"),"samples",sep=""))$case[tempcellcodes$libcodes])
  tempcellcodes$batch <- str_extract(batch,"Batch[[:digit:]]+")
  return(tempcellcodes)
}

metadata <- bind_rows(lapply(Batches,createmetadata), .id = "column_label")


```


```{r}

BatchMTG <- CreateSeuratObject(counts = do.call(cbind,lapply(Batches,get)),
                            project = "BatchMB_MTG",
                            min.cells = 3)
```


```{R}

BatchMTG@meta.data$sample_id <- metadata$samples
BatchMTG@meta.data$case <- metadata$case
BatchMTG@meta.data$batch <- metadata$batch

```




Now let's see the cell the counts for each group:
```{r}
table(BatchMTG$sample_id)
```

```{R}
table(BatchMTG$case)
```


 Quality Checking : 

 Seurat allows you to easily explore QC metrics and filter cells based on any user-defined criteria.
 A few QC metrics commonly used by the community include : 
 The number of unique genes detected in each cell.
 Low-quality cells or empty droplets will often have very few genes
 Cell doublets or multiplets may exhibit an aberrantly high gene count
 Similarly, the total number of molecules detected within a cell (correlates strongly with unique genes)
 The percentage of reads that map to the mitochondrial genome
 Low-quality / dying cells often exhibit extensive mitochondrial contamination
 We calculate mitochondrial QC metrics with the PercentageFeatureSet() function, which calculates the percentage of counts originating from a set of features
 We use the set of all genes starting with MT- as a set of mitochondrial genes

```{r}
BatchMB_MTG[["percent.mt"]] <- PercentageFeatureSet(BatchMB_MTG, pattern = "^MT-")

VlnPlot(BatchMB_MTG, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)


average nfeature_RNA

```{R}

library(stats)
nfeature_RNA <- BatchMTG@meta.data$nFeature_RNA
mean(nfeature_RNA)
MAD <- mad(nfeature_RNA, center = median(nfeature_RNA))
threeMAD <- (MAD*3)+median(BatchMTG@meta.data$nFeature_RNA)

```


Filtering low quality cells:
```{r}
BatchMB_MTG <- subset(BatchMB_MTG, subset = nFeature_RNA > 200 & nFeature_RNA < threeMAD & percent.mt < 5)
```


Log Normalizing data: 
```{r}
BatchMB_MTG <- NormalizeData(BatchMB_MTG, normalization.method = "LogNormalize", scale.factor = 10000)
```


Finding and plotting 2000 most variable features

```{R}
BatchMB_MTG <- FindVariableFeatures(BatchMB_MTG, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(BatchMB_MTG), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(BatchMB_MTG)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
```

```{R}
plot1
```

```{R}
plot2
```

Run the standard workflow for visualization and clustering :

save list of all genes
```{r}
all.genes <- rownames(BatchMB_MTG)
```

center and scale data
```{r}
BatchMB_MTG <- ScaleData(BatchMB_MTG, features = all.genes, verbose = FALSE)
```

Determining "Dimensionality" of the dataset





finding the top 30 principal components for cells
```{r}
BatchMB_MTG <- RunGLMPCA(BatchMB_MTG, features=BatchMB_MTG@assays$RNA@var.features, L = 30)
```

see contribution of genes to construct each of these principal components.
```{r}
VizDimLoadings(BatchMB_MTG, dims = 1:2, reduction = "pca")
```


plot cells in the first two principal components colored by case: 
```{r}
DimPlot(object = MTGandMidbrainIntegration, reduction = "pca", pt.size = .1, group.by = "case")
```

Coordinate of cells in PC 1 characterized by case: 
```{r}
VlnPlot(object = MTGandMidbrainIntegration, features = "PC_1", group.by = "case",  pt.size = .1)
```
#MTGandMidbrainIntegration <- RunHarmony(MTGandMidbrainIntegration, group.by.vars = c("case","region"), plot_convergence = TRUE)

Run Harmony

```{r}
BatchMB_MTG <- RunHarmony(BatchMB_MTG, group.by.vars = c("sample_id","case"), plot_convergence = TRUE, reduction = "glmpca", theta = c(1,1))
```


cells in harmony axis
```{r}
harmony_embeddings <- Embeddings(BatchMB_MTG, 'harmony')
harmony_embeddings[1:5, 1:5]
```

cells in harmony axis
```{r}
DimPlot(object = BatchMB_MTG,  reduction = "harmony", pt.size = .1, group.by = "case")
```
cells in harmony 1 axis
```{r}
VlnPlot(object = BatchMB_MTG, features = "harmony_1", group.by = "case",  pt.size = .1)
```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)
 2 dimensional reductions calculated: pca, harmony

Determing the dimensionality of the dataset

```{R}
#MTGandMidbrainIntegration <- JackStraw(MTGandMidbrainIntegration, num.replicate = 100)
#MTGandMidbrainIntegration <- ScoreJackStraw(MTGandMidbrainIntegration, dims = 1:12)
#JackStrawPlot(MTGandMidbrainIntegration, dims = 1:20)



```

```{R}

ElbowPlot(BatchMB_MTG, reduction = "glmpca")

```

```{R}

ElbowPlot(BatchMB_MTG, reduction = "harmony")

```

```{R}
saveRDS(BatchMB_MTG,"Files/MTGandFullMidbrainIntegration_precluster.rds")

BatchMB_MTG <- readRDS("Files/MTGandFullMidbrainIntegration_precluster.rds")
```

10 looks like a suitable cutoff based on the elbow plot, but the JackStraw plot looks very strange

Finding Clusters of cells:
```{r}
BatchMB_MTG <- FindNeighbors(BatchMB_MTG, reduction = "harmony", dims = 1:20)
BatchMB_MTG <- FindClusters(BatchMB_MTG, resolution = 0.5, algorithm = 4, method = "igraph")
```

run Umap based on top 10 harmony axis: 

```{r}
BatchMB_MTG <- RunUMAP(BatchMB_MTG, reduction = "harmony", dims = 1:20)
```

run tsne based on top 10 harmony axis: 

```{r}
#MTGandMidbrainIntegration <- RunTSNE(MTGandMidbrainIntegration, reduction = "harmony", dims = 1:17)
```

plot umap: 
```{r}
DimPlot(BatchMB_MTG, reduction = "umap", label = TRUE,pt.size = 0.01)
```

```{r}
DimPlot(BatchMB_MTG, reduction = "umap", group.by = "case",pt.size = 0.1)
```

```{r}

BatchMB_MTG@meta.data$region <- "Midbrain"

BatchMB_MTG@meta.data$region[BatchMB_MTG@meta.data$batch %in% c("Batch7","Batch8")] <- "MTG"

DimPlot(BatchMB_MTG, reduction = "umap", group.by = "region",pt.size = 0.1)

```


TSNE Plot cells colored by clusters and grouped by case. 
```{r}
DimPlot(BatchMB_MTG, reduction = "umap", split.by = "case", label = TRUE, ncol = 1)
```

```{r}
DimPlot(BatchMB_MTG, reduction = "umap", split.by = "region", label = TRUE, ncol = 1)
```


```{R}

MTGandMidbrainIntegration_UMAP_Clusters <- DimPlot(BatchMB_MTG, reduction = "umap", label = TRUE, pt.size = 0.01) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_UMAP_Clusters, filename = "Figures/MTGandMidbrainIntegration_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 4, units = "in")

MTGandMidbrainIntegration_Case_Group_UMAP_Clusters <- DimPlot(BatchMB_MTG, reduction = "umap", group.by = "case",pt.size = 0.1) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Case_Group_UMAP_Clusters, filename = "Figures/MTGandMidbrainIntegration_Case_Group_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 4, units = "in")

MTGandMidbrainIntegration_Region_Group_UMAP_Clusters <- DimPlot(BatchMB_MTG, reduction = "umap", group.by = "region",pt.size = 0.1) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Region_Group_UMAP_Clusters, filename = "Figures/MTGandMidbrainIntegration_Region_Group_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 4, units = "in")

MTGandMidbrainIntegration_Case_Split_UMAP_Clusters <- DimPlot(BatchMB_MTG, reduction = "umap", split.by = "case", label = TRUE, ncol = 1) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Case_Split_UMAP_Clusters, filename = "Figures/MTGandMidbrainIntegration_Case_Split_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 8, units = "in")

MTGandMidbrainIntegration_Region_Split_UMAP_Clusters <- DimPlot(BatchMB_MTG, reduction = "umap", split.by = "region", label = TRUE, ncol = 1) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Region_Split_UMAP_Clusters, filename = "Figures/MTGandMidbrainIntegration_Region_Split_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 8, units = "in")

```

Find markers for every cluster compared to all remaining cells, report only the positive ones
```{r}
MTGandMidbrainIntegration.markers <- FindAllMarkers(MTGandMidbrainIntegration, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
```


Save single-cell elements. 
```{r}
#saveRDS(MTGandMidbrainIntegration,"Files/MTGandMidbrainIntegrationClusteredUnassiged.rds")
```

```{r}
#MTGandMidbrainIntegration <- readRDS("Files/MTGandMidbrainIntegrationClusteredUnassiged.rds")
```

```{r}
#saveRDS(AllMB.markers,"AllMB.markers.rds")
```

```{r}
#AllMB.markers=readRDS("AllMB.markers.rds")
#write.csv(AllMB.markers,"AllMB_markers.csv")
```

```{r}
unique(MTGandMidbrainIntegration.markers$cluster)
```

Top marker genes for each clusters: 
```{r}
MTGandMidbrainIntegration.markers %>% group_by(cluster) %>% top_n(n = 2, wt = avg_log2FC)
write.table(MTGandMidbrainIntegration.markers, file = "Files/AllMarkers.txt", col.names = TRUE, sep = "\t", quote = FALSE)
top10Markers <- MTGandMidbrainIntegration.markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_log2FC)
write.table(top10Markers, file = "Files/top10Markers.txt", col.names = TRUE, sep = "\t", quote = FALSE)
```

Heatmap for some marker genes: 
```{r}
features <- unique(top10Markers$gene)
DoHeatmap(MTGandMidbrainIntegration, features = features, size = 2, draw.lines = FALSE, angle = 45,
          hjust = 0.2) + theme(axis.text.y = element_text(size = 5))
```
#ignore actual genes, this is just a reminder of what a FeaturePlot is 

Plot these genes in the cluster plot:
```{r}
FeaturePlot(MTGandMidbrainIntegration, features = c("ENO2", "RBFOX3","SLC17A6", "SLC17A7","AQP4", "GFAP"))
```

```{r}
saveRDS(MTGandMidbrainIntegration,"Files/MTGandMidbrainIntegrationClusteredUnassiged.rds")
```


 
#########################################################
 
```{R}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
```
 
 
 
 
```{R}
MTGandMidbrainIntegration=readRDS("Files/MTGandMidbrainIntegrationClusteredUnassiged.rds")
```
 
Testing T-cell/immune cell markers




```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("CD96"),pt.size = 0, split.by = "region")
```
NK Cell Markers

```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("IL7R"),pt.size = 0, split.by = "region")
```


CD16

```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("FCGR3A"),pt.size = 0)
```

CD56

```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("NCAM1"),pt.size = 0)
```

CD94


```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("KLRD1"),pt.size = 0)
```
NKG2A

```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("KLRC1"),pt.size = 1)
```
```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("CD244"),pt.size = 0)
```

resting T cell marker?


```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("CD8A"),pt.size = 1)
```

```{r}
TKillerCellMarkerVlnPlot <- VlnPlot(AllMB, features = c("CD8A","CD226","CD244","CD96","IL7R","KLRD1","NCAM1","FCGR3A","KLRC1"),pt.size = 0, ncol = 1) 

ggsave(TKillerCellMarkerVlnPlot,filename = "TKillerCellMarkerVlnPlot.pdf", width = 20, height = 20)            


```


##################################################################

T lymphocyte markers

```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("CD69"),pt.size = 0)
```



```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("TFRC"),pt.size = 0)
```



```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("IL2RA"),pt.size = 0)
```



```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("CTLA4"),pt.size = 0)
```



```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("FOXP3"),pt.size = 0)
```

```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("TRAC"),pt.size = 0)
```


###################################################################

 Neuron  = ENO2, RBFOX3
 Glutamatergic neurons = SLC17A6, SLC17A7
 GABAergic neurons = SLC32A1, GAD1, GAD2
 Dopaminergic neurons = TH, SLC6A3, SCL18A2
 Astrocytes  = AQP4, GFAP
 Oligodendrocytes  =  PLP1, MBP
 OPCs  =  VCAN, BCAN,
 Microglia = CX3CR1, P2RY12
 Endothelial cells = FLT1, CLDN5
 
Dopaminergic: 21
 Glu_Neurons = 1,3,7,8,9,11,14,17,18,19,20,23
 GABA_Neurons = 4,6,13,24
 Astrocytes = 5
 oligo = 2,22
 OPCs= 12
 Microglia = 10
 Endothelial = 15,16
 overlapping = 4
 novel = 5,11,12,13,14 - all likely neurons

Find cell-types by plotting marker genes.

Neuron Markers

```{r}
VlnPlot(MTGandMidbrainIntegration, features = c("ENO2"),pt.size = 0)
```
Neurons: 0,1,2,3,5,6,7,8,9,10,13,15,16,18


```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("RBFOX3"),pt.size = 0)
```
Dopaminergic neuron markers

```{R}
VlnPlot(BatchMB_MTG, features = c("SLC6A3"),pt.size = 1, split.by = "region")
```

```{R}
VlnPlot(BatchMB_MTG, features = c("SLC18A2"),pt.size = 1)
```

```{R}
VlnPlot(BatchMB_MTG, features = c("TH"),pt.size = 1)

VlnPlot(BatchMB_MTG, features = c("TH"),pt.size = 1, split.by = "region")
```

DA neurons 12, (14)

Glutamatergic neuron markers

```{R}
VlnPlot(BatchMB_MTG, features = c("SLC17A6"),pt.size = 1, split.by = "region")
```
```{R}
VlnPlot(BatchMB_MTG, features = c("SLC17A7"),pt.size = 1)
```
0,1,2,6,10,(14),19,21,22,23,26 - Glu?

GABAergic markers



```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("SLC32A1"),pt.size = 1)
```



```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("GAD1"),pt.size = 1)
```


```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("GAD2"),pt.size = 1)
```

7,11,12,16,20,24 - GABA?



Astrocyte markers

```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("AQP4"),pt.size = 0)
```


```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("GFAP"),pt.size = 0)
```
```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("ALDH1L1"),pt.size = 0)
```
ALDH1L1



8,13 - Astrocytes

Oligodendrocyte markers


```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("PLP1"),pt.size = 0)
```

```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("MBP"),pt.size = 0)
```


```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("MOG"),pt.size = 1)
```

3,4,5,17 - oligodendrocytes - strong



OPC markers

```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("VCAN"),pt.size = 0)
```
```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("BCAN"),pt.size = 0)
```

16,24 - OPCs

Microglia

```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("CX3CR1"),pt.size = 0)
```

```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("P2RY12"),pt.size = 0)
```

9 - Microglia

Endothelial Cells

```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("FLT1"),pt.size = 0)
```


```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("CLDN5"),pt.size = 0)
```
15,18 - Endothelial cells

 Neuron  = ENO2, RBFOX3
 Glutamatergic neurons = SLC17A6, SLC17A7
 GABAergic neurons = SLC32A1, GAD1, GAD2
 Dopaminergic neurons = TH, SLC6A3, SCL18A2
 Astrocytes  = AQP4, GFAP
 Oligodendrocytes  =  PLP1, MBP
 OPCs  =  VCAN, BCAN,
 Microglia = CX3CR1, P2RY12
 Endothelial cells = FLT1, CLDN5
 
 Alter to make it counts per million

```{R}
library(reshape2)
library(sciplot)
library(ggplot2)

MarkerGenes <- c("ENO2","RBFOX3","SLC17A6","SLC17A7","SLC32A1","GAD1","GAD2","AQP4","GFAP","PLP1","MBP","VCAN","BCAN","CX3CR1","P2RY12","FLT1","CLDN5")

data_barplot <- FetchData(MTGandMidbrainIntegration, vars = c("ident",rownames(MTGandMidbrainIntegration@assays$RNA@counts)), slot = "counts")

data_barplot_1 <- data_barplot[1:10,]

#rowSums(data_barplot_1[2:length(colnames(data_barplot_1))])

#1e6/rowSums(data_barplot_1[2:length(colnames(data_barplot_1))])

scaledrowSums <- 1e6/rowSums(data_barplot[2:length(colnames(data_barplot))])

swpt_barplot <- sweep(data_barplot[,2:length(colnames(data_barplot))],1,scaledrowSums,FUN = "*")

swpt_data_barplot_markers <- swpt_barplot[,which(colnames(swpt_barplot) %in% MarkerGenes)]

swpt_data_barplot_markers$ident <- as.vector(data_barplot$ident)

data_barplot_melt <- melt(swpt_data_barplot_markers)

data_barplot_melt$ident <- as.vector(data_barplot_melt$ident)
data_barplot_melt$variable <- as.vector(data_barplot_melt$variable)
data_barplot_melt$value <- as.numeric(as.vector(data_barplot_melt$value))

data_barplot_melt_sum <- group_by(data_barplot_melt,ident,variable) %>% summarise(mean = mean(value), SE = se(value))

data_barplot_melt_sum$ident <- factor(data_barplot_melt_sum$ident, levels = unique(data_barplot_melt_sum$ident))

data_barplot_melt_sum$variable <- factor(data_barplot_melt_sum$variable, levels = unique(MarkerGenes))

ggplot(data_barplot_melt_sum, aes(x = ident, y = mean, fill = ident)) + 
        geom_bar(aes(x = ident, y = mean), stat = "identity", alpha = 1) + 
        geom_errorbar(aes(x = ident, ymin = mean-SE, ymax = mean+SE, colour = ident), width = 0.4, alpha = 0.9, size = 0.5) + 
        ggplot2::facet_grid(rows = vars(variable), scales = "free_y", switch = "y") + 
        theme(axis.title = element_blank(), axis.text.x = element_text(size = 12, angle = 45, face = "bold", vjust = 0.5),
              axis.text.y = element_blank(), axis.ticks = element_blank(), panel.background = element_blank(),
              strip.background = element_blank(), strip.placement = "outside", 
              strip.text.y = element_text(size = 12, angle = 180, face = "bold"),
              strip.text.y.left = element_text(angle = 0)) + NoLegend()



Batch8_barchart <- ggplot(data_barplot_melt_sum, aes(x = ident, y = mean, fill = ident)) + 
        geom_bar(aes(x = ident, y = mean), stat = "identity", alpha = 1) + 
        geom_errorbar(aes(x = ident, ymin = mean-SE, ymax = mean+SE, colour = ident), width = 0.4, alpha = 0.9, size = 0.5) + 
        ggplot2::facet_grid(rows = vars(variable), scales = "free_y", switch = "y") + 
        theme(axis.title = element_blank(), axis.text.x = element_text(size = 12, angle = 45, face = "bold", vjust = 0.5),
              axis.text.y = element_blank(), axis.ticks = element_blank(), panel.background = element_blank(),
              strip.background = element_blank(), strip.placement = "outside", 
              strip.text.y = element_text(size = 12, angle = 180, face = "bold"),
              strip.text.y.left = element_text(angle = 0)) + NoLegend()


ggsave(Batch8_barchart,filename = "Files/Batch8_Marker_Barchart", device = "pdf", width = 12, height = 12, units = "in")
```
1,2,3,5,10

Alternate way of creating the barplot matrix

###







###




################################################################################################################

Reading in the table for panglaodb to more systematically go through the known types of brain cell and assess their presence in the dataset.

```{R}
#PanglaoDB <- read.delim("~/Documents/Projects/Misc. Files/PanglaoDB_markers_27_Mar_2020.tsv", stringsAsFactors = FALSE)

#PanglaoDBBrain <- PanglaoDB[PanglaoDB$organ %in% "Brain",]
```

Let's see how many unique cell types for the brain the database contains

```{R}
#unique(PanglaoDBBrain$cell.type)

#sum(is.na(PanglaoDBBrain$cell.type))
```
Reminder of the unnassigned clusters:

novel = 7,12,14,15,19,21 - all neurons

Looking at top 5 markers for each cell type

Making function and testing

```{R}
#GeneSet <- rownames(GetAssayData(object = MTGandMidbrainIntegration, assay.type = "RNA", slot = "counts"))

#filtering PanglaoDB for genes present in the scRNA-seq dataset

#PanglaoDBBrainGroupfilter <- PanglaoDBBrainGroup[PanglaoDBBrainGroup$official.gene.symbol %in% GeneSet,]

#markervlnplots <- function(x) {
#  VlnPlot(MTGandMidbrainIntegration, features = x,pt.size = 0)
  
#}

#markervlnplots("RELN")

```



Running function for Tancytes

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Tanycytes",]$official.gene.symbol,markervlnplots)
```

Glycinergic neurons

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Glycinergic neurons",]$official.gene.symbol,markervlnplots)
```

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Noradrenergic neurons",]$official.gene.symbol,markervlnplots)
```
```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Serotonergic neurons",]$official.gene.symbol,markervlnplots)
```

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Trigeminal neurons",]$official.gene.symbol,markervlnplots)
```

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Pyramidal cells",]$official.gene.symbol,markervlnplots)
```


Running function through lapply for all cell types in the brain in PanglaoDB

```{R}
#lapply(unique(PanglaoDBBrain$cell.type), markervlnplots, y=PanglaoDBBrain)



```









Other form of ploting genes across clusters:
```{r}
#RidgePlot(AllMB, features=c("ENO2"))
#RidgePlot(AllMB, features=c("TH"))
#RidgePlot(AllMB, features=c("SLC6A3"))
#RidgePlot(AllMB, features=c("SLC18A2"))
#RidgePlot(AllMB, features=c("SLC17A6"))
#RidgePlot(AllMB, features=c("GAD2"))
```


##################################################################################################

```{R}
VlnPlot(MTGandMidbrainIntegration, features = c("CLDN5","TH","P2RY12","GRM4","BCAN"),pt.size = 0,stack = TRUE, flip = TRUE)
```

0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,26

Dopaminergic: 21
 Glu_Neurons = 1,3,7,8,9,11,14,17,18,19,20,23
 GABA_Neurons = 4,6,13,24
 Astrocytes = 5
 oligo = 2,22
 OPCs= 12
 Microglia = 10
 Endothelial = 15,16


Assigning cell type identity to clusters: 

```{r}
BatchMB_MTG <- RenameIdents(BatchMB_MTG, `1` = "GLU Neurons", `2` = "Oligodendrocytes",
                      `3` = "GLU Neurons", `4` = "GABA Neurons", `5` = "Astrocytes",
                      `6` = "GABA Neurons", `7` = "GLU Neurons", `8` = "GLU Neurons",`9` = "GLU Neurons",
                      `10` = "Microglia", `11` = "GLU Neurons",`12` = "OPCs",
                      `13` = "GABA Neurons",`14` = "GLU Neurons",
                      `15` = "Endothelial", `16`="Endothelial", `17`="GLU Neurons", `18`="GLU Neurons", `19`="GLU Neurons",  `20`="GLU Neurons", `21` = "DA Neurons", `22` = "Oligodendrocytes", `23` = "GLU Neurons", `24` = "GABA Neurons")
```

reminder:, `25` = "CD8+ T cells", `25` = "GLU Neurons",`26` = "GLU Neurons"

```{R}
#saveRDS(AllMB,"AllMB_Assigned.rds")
#AllMB=readRDS("AllMB.rds")
```

```{R}

#AllMB <- readRDS("Files/AllMB_Assigned.rds")

```



Now let's plot cells with the assigned celltypes: 
```{r}
DimPlot(BatchMB_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2)

UMAPclusters <- DimPlot(BatchMB_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Files/Assigned_UMAPclusters_scRNA_seq_MTGandMidbrainIntegration.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

```{r}
DimPlot(BatchMB_MTG, reduction = "umap", group.by = "case",pt.size = 0.1)
```

```{r}
DimPlot(MTGandMidbrainIntegration, reduction = "umap", group.by = "region",pt.size = 0.1)
```


TSNE Plot cells colored by clusters and grouped by case. 
```{r}
DimPlot(MTGandMidbrainIntegration, reduction = "umap", split.by = "case", label = TRUE, ncol = 1)
```

```{r}
DimPlot(BatchMB_MTG, reduction = "umap", split.by = "region", label = TRUE, ncol = 1)
```


```{R}
MTGandMidbrainIntegration_UMAP_Clusters <- DimPlot(MTGandMidbrainIntegration, reduction = "umap", label = TRUE, pt.size = 0.01, label.size = 2.5) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = ),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_UMAP_Clusters, filename = "Figures/Assigned_MTGandMidbrainIntegration_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 4, units = "in")

MTGandMidbrainIntegration_Case_Group_UMAP_Clusters <- DimPlot(MTGandMidbrainIntegration, reduction = "umap", group.by = "case",pt.size = 0.1, label.size = 2.5) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Case_Group_UMAP_Clusters, filename = "Figures/Assigned_MTGandMidbrainIntegration_Case_Group_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 4, units = "in")

MTGandMidbrainIntegration_Region_Group_UMAP_Clusters <- DimPlot(MTGandMidbrainIntegration, reduction = "umap", group.by = "region",pt.size = 0.1, label.size = 2.5) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Region_Group_UMAP_Clusters, filename = "Figures/Assigned_MTGandMidbrainIntegration_Region_Group_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 4, units = "in")

MTGandMidbrainIntegration_Case_Split_UMAP_Clusters <- DimPlot(MTGandMidbrainIntegration, reduction = "umap", split.by = "case", label = TRUE, ncol = 1, label.size = 2.5) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Case_Split_UMAP_Clusters, filename = "Figures/Assigned_MTGandMidbrainIntegration_Case_Split_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 8, units = "in")

MTGandMidbrainIntegration_Region_Split_UMAP_Clusters <- DimPlot(MTGandMidbrainIntegration, reduction = "umap", split.by = "region", label = TRUE, ncol = 1, label.size = 2.5) + 
  theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(MTGandMidbrainIntegration_Region_Split_UMAP_Clusters, filename = "Figures/Assigned_MTGandMidbrainIntegration_Region_Split_UMAP_Clusters.pdf", device = "pdf", width = 6, height = 8, units = "in")

```



```{r}
DimPlot(MTGandMidbrainIntegration, label = TRUE, repel = TRUE, pt.size = 1, split.by = "case", label.size = 2,
        ncol = 1) + NoLegend()
```


```{r}
DimPlot(MTGandMidbrainIntegration, label = TRUE, repel = TRUE, pt.size = 1,reduction = 'umap')
```


```{R}
Markerggplots <- function(SeurObj,Genes){
  for (i in Genes) {
    TempViolin <- VlnPlot(SeurObj, features = i ,pt.size = 0)
    ggsave(TempViolin, filename = paste("Files/",i,"_VlnPlot.pdf",sep = ""), device = "pdf", width = 12, height = 4, units = "in")
}}

Markerggplots(MTGandMidbrainIntegration,MarkerGenes)


```

