---
title: "Seurat Workflow and Cluster Assignment for Batch 4"
output: html_document
---

```{R}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
```



Loading in the single cell data

```{r}
batch4.data <- Read10X(data.dir = "Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
```






checking dimensions to check all samples have the same set of genes

```{r}
dim(batch4.data)


```


```{r}
Batch4_MTG <- CreateSeuratObject(counts = cbind(batch4.data),
                            project = "Batch4_MTG",
                            min.cells = 3)
```


```{R}
samples <- read.csv(file.path("Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)

cellcodes <- as.data.frame(Batch4_MTG@assays$RNA@data@Dimnames[[2]])
colnames(cellcodes) <- "barcodes"
rownames(cellcodes) <- cellcodes$barcodes

cellcodes$libcodes <- as.factor(gsub(pattern=".+-", replacement="", cellcodes$barcodes))
cellcodes$samples <- as.vector(samples$library_id[cellcodes$libcodes])

Batch4_MTG@meta.data$sample_ID <- cellcodes$samples



```


```{R}
samples$case <- c("HC","HC","PD","ILBD")

cellcodes$case <- as.vector(samples$case[cellcodes$libcodes])

Batch4_MTG@meta.data$case <- cellcodes$case

```




Now let's see the cell the counts for each group:
```{r}
table(Batch4_MTG$sample_ID)
```

```{R}
table(Batch4_MTG$case)
```


 Quality Checking : 

 Seurat allows you to easily explore QC metrics and filter cells based on any user-defined criteria.
 A few QC metrics commonly used by the community include : 
 The number of unique genes detected in each cell.
 Low-quality cells or empty droplets will often have very few genes
 Cell doublets or multiplets may exhibit an aberrantly high gene count
 Similarly, the total number of molecules detected within a cell (correlates strongly with unique genes)
 The percentage of reads that map to the mitochondrial genome
 Low-quality / dying cells often exhibit extensive mitochondrial contamination
 We calculate mitochondrial QC metrics with the PercentageFeatureSet() function, which calculates the percentage of counts originating from a set of features
 We use the set of all genes starting with MT- as a set of mitochondrial genes

```{r}
Batch4_MTG[["percent.mt"]] <- PercentageFeatureSet(Batch4_MTG, pattern = "^MT-")

VlnPlot(Batch4_MTG, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)


average nfeature_RNA

```{R}
library(stats)
nfeature_RNA <- Batch4_MTG@meta.data$nFeature_RNA
mean(nfeature_RNA)
MAD <- mad(nfeature_RNA, center = median(nfeature_RNA))
threeMAD <- (MAD*3)+median(Batch4_MTG@meta.data$nFeature_RNA)

```


Filtering low quality cells:
```{r}
Batch4_MTG <- subset(Batch4_MTG, subset = nFeature_RNA > 200 & nFeature_RNA > threeMAD | percent.mt < 5)
```

Now let's recheck the cell the counts for each group:
```{r}
table(Batch4_MTG$sample_ID)
```

```{R}
table(Batch4_MTG$case)
```


Log Normalizing data: 
```{r}
Batch4_MTG <- NormalizeData(Batch4_MTG, normalization.method = "LogNormalize", scale.factor = 10000)
```


Finding and plotting 2000 most variable features

```{R}
Batch4_MTG <- FindVariableFeatures(Batch4_MTG, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(Batch4_MTG), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(Batch4_MTG)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
```

```{R}
plot1
```

```{R}
plot2
```

Run the standard workflow for visualization and clustering :

save list of all genes
```{r}
all.genes <- rownames(Batch4_MTG)
```

center and scale data
```{r}
Batch4_MTG <- ScaleData(Batch4_MTG, features = all.genes, verbose = FALSE)
```

Determining "Dimensionality" of the dataset





finding the top 30 principal components for cells
```{r}
Batch4_MTG <- RunPCA(Batch4_MTG, npcs = 30, verbose = FALSE)
```

see contribution of genes to construct each of these principal components.
```{r}
VizDimLoadings(Batch4_MTG, dims = 1:2, reduction = "pca")
```


plot cells in the first two principal components colored by case: 
```{r}
DimPlot(object = Batch4_MTG, reduction = "pca", pt.size = .1, group.by = "case")
```

Coordinate of cells in PC 1 characterized by case: 
```{r}
VlnPlot(object = Batch4_MTG, features = "PC_1", group.by = "case",  pt.size = .1)
```

Run Harmony
```{r}
Batch4_MTG <- RunHarmony(Batch4_MTG, group.by.vars = "case", plot_convergence = TRUE)
```


cells in harmony axis
```{r}
harmony_embeddings <- Embeddings(Batch4_MTG, 'harmony')
harmony_embeddings[1:5, 1:5]
```

cells in harmony axis
```{r}
DimPlot(object = Batch4_MTG, reduction = "harmony", pt.size = .1, group.by = "case")
```
cells in harmony 1 axis
```{r}
VlnPlot(object = Batch4_MTG, features = "harmony_1", group.by = "case",  pt.size = .1)
```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)
 2 dimensional reductions calculated: pca, harmony

Determing the dimensionality of the dataset

```{R}
#Batch4_MTG <- JackStraw(Batch4_MTG, num.replicate = 100)
#Batch4_MTG <- ScoreJackStraw(Batch4_MTG, dims = 1:12)
#JackStrawPlot(Batch4_MTG, dims = 1:20)



```
```{R}
ElbowPlot(Batch4_MTG)

```
10 looks like a suitable cutoff based on the elbow plot, but the JackStraw plot looks very strange

Finding Clusters of cells:
```{r}
Batch4_MTG <- FindNeighbors(Batch4_MTG, reduction = "harmony", dims = 1:12)
Batch4_MTG <- FindClusters(Batch4_MTG, resolution = 0.5)
```

run Umap based on top 10 harmony axis: 

```{r}
Batch4_MTG <- RunUMAP(Batch4_MTG, reduction = "harmony", dims = 1:12)
```

run tsne based on top 10 harmony axis: 

```{r}
Batch4_MTG <- RunTSNE(Batch4_MTG, reduction = "harmony", dims = 1:12)
```

plot umap: 
```{r}
DimPlot(Batch4_MTG, reduction = "umap", label = TRUE,pt.size = 0.01)
```

```{r}
DimPlot(Batch4_MTG, reduction = "umap", group.by = "case",pt.size = 0.1)
```
TSNE Plot cells colored by clusters and grouped by case. 
```{r}
DimPlot(Batch4_MTG, reduction = "umap", split.by = "case", label = TRUE, ncol = 1)
```

```{r}
Batch4_MTG_Case_UMAP <- DimPlot(Batch4_MTG, reduction = "umap", split.by = "case", label = TRUE, ncol = 1) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(Batch4_MTG_Case_UMAP, filename = "Figures/Batch4_MTG_Case_UMAP.pdf", device = "pdf", width = 6, height = 8, units = "in")
```


TSNE Plot cells colored by clusters and grouped by case. 
```{r}
Batch4_MTG_Case_tsne <- DimPlot(Batch4_MTG, reduction = "tsne", split.by = "case", label = TRUE, ncol = 1) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(Batch4_MTG_Case_tsne, filename = "Figures/Batch4_MTG_Case_tsne.pdf", device = "pdf", width = 6, height = 8, units = "in")
```

Find markers for every cluster compared to all remaining cells, report only the positive ones
```{r}
Batch4_MTG.markers <- FindAllMarkers(Batch4_MTG, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
```


Save single-cell elements. 
```{r}
#saveRDS(AllMB,"AllMB.rds")
```

```{r}
#AllMB=readRDS("AllMB.rds")
```

```{r}
#saveRDS(AllMB.markers,"AllMB.markers.rds")
```

```{r}
#AllMB.markers=readRDS("AllMB.markers.rds")
#write.csv(AllMB.markers,"AllMB_markers.csv")
```

```{r}
unique(Batch4_MTG.markers$cluster)
```

Top marker genes for each clusters: 
```{r}
Batch4_MTG.markers %>% group_by(cluster) %>% top_n(n = 2, wt = avg_log2FC)
write.table(Batch4_MTG.markers, file = "Files/AllMarkers.txt", col.names = TRUE, sep = "\t", quote = FALSE)
top10Markers <- Batch4_MTG.markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_log2FC)
write.table(top10Markers, file = "Files/top10Markers.txt", col.names = TRUE, sep = "\t", quote = FALSE)
```

Heatmap for some marker genes: 
```{r}
features <- unique(top10Markers$gene)
DoHeatmap(Batch4_MTG, features = features, size = 2, draw.lines = FALSE, angle = 45,
          hjust = 0.2) + theme(axis.text.y = element_text(size = 5))
```
#ignore actual genes, this is just a reminder of what a FeaturePlot is 

Plot these genes in the cluster plot:
```{r}
FeaturePlot(Batch4_MTG, features = c("ENO2", "RBFOX3","SLC17A6", "SLC17A7","AQP4", "GFAP"))
```

```{r}
#saveRDS(AllMB,"AllMB_Unassigned.rds")
```


 
 #########################################################
 
```{R}
#AllMB=readRDS("AllMB_Assigned.rds")
```
 
Testing T-cell/immune cell markers




```{r}
VlnPlot(Batch4_MTG, features = c("CD96"),pt.size = 0)
```
NK Cell Markers

```{r}
VlnPlot(Batch4_MTG, features = c("IL7R"),pt.size = 0)
```


CD16

```{r}
VlnPlot(Batch4_MTG, features = c("FCGR3A"),pt.size = 0)
```

CD56

```{r}
VlnPlot(Batch4_MTG, features = c("NCAM1"),pt.size = 0)
```

CD94


```{r}
VlnPlot(Batch4_MTG, features = c("KLRD1"),pt.size = 0)
```
NKG2A

```{r}
VlnPlot(Batch4_MTG, features = c("KLRC1"),pt.size = 0)
```
```{r}
VlnPlot(Batch4_MTG, features = c("CD244"),pt.size = 0)
```

resting T cell marker?


```{r}
VlnPlot(Batch4_MTG, features = c("CD8A"),pt.size = 0)
```

```{r}
TKillerCellMarkerVlnPlot <- VlnPlot(AllMB, features = c("CD8A","CD226","CD244","CD96","IL7R","KLRD1","NCAM1","FCGR3A","KLRC1"),pt.size = 0, ncol = 1) 

ggsave(TKillerCellMarkerVlnPlot,filename = "TKillerCellMarkerVlnPlot.pdf", width = 20, height = 20)            


```


##################################################################

T lymphocyte markers

```{r}
VlnPlot(Batch4_MTG, features = c("CD69"),pt.size = 0)
```



```{r}
VlnPlot(Batch4_MTG, features = c("TFRC"),pt.size = 0)
```



```{r}
VlnPlot(Batch4_MTG, features = c("IL2RA"),pt.size = 0)
```



```{r}
VlnPlot(Batch4_MTG, features = c("CTLA4"),pt.size = 0)
```



```{r}
VlnPlot(Batch4_MTG, features = c("FOXP3"),pt.size = 0)
```

```{r}
VlnPlot(Batch4_MTG, features = c("TRAC"),pt.size = 0)
```


###################################################################

 Neuron  = ENO2, RBFOX3
 Glutamatergic neurons = SLC17A6, SLC17A7
 GABAergic neurons = SLC32A1, GAD1, GAD2
 Dopaminergic neurons = TH, SLC6A3, SCL18A2
 Astrocytes  = AQP4, GFAP
 Oligodendrocytes  =  PLP1, MBP
 OPCs  =  VCAN, BCAN,
 Microglia = CX3CR1, P2RY12
 Endothelial cells = FLT1, CLDN5
 

 Glu_Neurons = 1,3,(10),17
 GABA_Neurons = 6,7,16
 Astrocytes = 4,18
 oligo = 0,2
 OPCs= 4,9
 Microglia = 8
 Endothelial = 15
 overlapping = 4
 novel = 5,11,12,13,14 - all likely neurons

Find cell-types by plotting marker genes.

Neuron Markers

```{r}
VlnPlot(Batch4_MTG, features = c("ENO2"),pt.size = 0)
```
Neurons: 1,4,5,6,7,9,11,12,13,14,15,16,19,20,21


```{R}
VlnPlot(Batch4_MTG, features = c("RBFOX3"),pt.size = 0)
```

Glutamatergic neuron markers

```{R}
VlnPlot(Batch4_MTG, features = c("SLC17A6"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("SLC17A7"),pt.size = 0)
```
4,5,13,17,19,21 - Glu?

GABAergic markers



```{R}
VlnPlot(Batch4_MTG, features = c("SLC32A1"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("GAD1"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("GAD2"),pt.size = 0)
```
9,10,12,14 - GABA?

weaker evidence for 10

Astrocyte markers
```{R}
VlnPlot(Batch4_MTG, features = c("AQP4"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("GFAP"),pt.size = 0)
```
7,(18,20) - Astrocytes

Oligodendrocyte markers


```{R}
VlnPlot(Batch4_MTG, features = c("PLP1"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("MBP"),pt.size = 0)
```


```{R}
VlnPlot(Batch4_MTG, features = c("MOG"),pt.size = 0)
```

0,3 - oligodendrocytes - strong



OPC markers

```{R}
VlnPlot(Batch4_MTG, features = c("VCAN"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("BCAN"),pt.size = 0)
```

16 - OPCs

Microglia

```{R}
VlnPlot(Batch4_MTG, features = c("CX3CR1"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("P2RY12"),pt.size = 0)
```

11 - Microglia

Endothelial Cells

```{R}
VlnPlot(Batch4_MTG, features = c("FLT1"),pt.size = 0)
```
```{R}
VlnPlot(Batch4_MTG, features = c("CLDN5"),pt.size = 0)
```
18,20 - Endothelial cells

################################################################################################################

Reading in the table for panglaodb to more systematically go through the known types of brain cell and assess their presence in the dataset.

```{R}
#PanglaoDB <- read.delim("~/Documents/Projects/Misc. Files/PanglaoDB_markers_27_Mar_2020.tsv", stringsAsFactors = FALSE)

#PanglaoDBBrain <- PanglaoDB[PanglaoDB$organ %in% "Brain",]
```

Let's see how many unique cell types for the brain the database contains

```{R}
#unique(PanglaoDBBrain$cell.type)

#sum(is.na(PanglaoDBBrain$cell.type))
```
Reminder of the unnassigned clusters:

novel = 7,12,14,15,19,21 - all neurons

Looking at top 5 markers for each cell type

Making function and testing

```{R}
#GeneSet <- rownames(GetAssayData(object = Batch4_MTG, assay.type = "RNA", slot = "counts"))

#filtering PanglaoDB for genes present in the scRNA-seq dataset

#PanglaoDBBrainGroupfilter <- PanglaoDBBrainGroup[PanglaoDBBrainGroup$official.gene.symbol %in% GeneSet,]

#markervlnplots <- function(x) {
#  VlnPlot(Batch4_MTG, features = x,pt.size = 0)
  
#}

#markervlnplots("RELN")

```



Running function for Tancytes

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Tanycytes",]$official.gene.symbol,markervlnplots)
```

Glycinergic neurons

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Glycinergic neurons",]$official.gene.symbol,markervlnplots)
```

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Noradrenergic neurons",]$official.gene.symbol,markervlnplots)
```
```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Serotonergic neurons",]$official.gene.symbol,markervlnplots)
```

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Trigeminal neurons",]$official.gene.symbol,markervlnplots)
```

```{R}
#lapply(PanglaoDBBrainGroupfilter[PanglaoDBBrainGroupfilter$cell.type %in% "Pyramidal cells",]$official.gene.symbol,markervlnplots)
```


Running function through lapply for all cell types in the brain in PanglaoDB

```{R}
#lapply(unique(PanglaoDBBrain$cell.type), markervlnplots, y=PanglaoDBBrain)



```









Other form of ploting genes across clusters:
```{r}
#RidgePlot(AllMB, features=c("ENO2"))
#RidgePlot(AllMB, features=c("TH"))
#RidgePlot(AllMB, features=c("SLC6A3"))
#RidgePlot(AllMB, features=c("SLC18A2"))
#RidgePlot(AllMB, features=c("SLC17A6"))
#RidgePlot(AllMB, features=c("GAD2"))
```


##################################################################################################

```{R}
VlnPlot(Batch4_MTG, features = c("CLDN5","TH","P2RY12","GRM4","BCAN"),pt.size = 0,stack = TRUE, flip = TRUE)
```




 Glu_Neurons = 4,5,13,17,19,21
 GABA_Neurons = 9,10,12,14
 Astrocytes = 7
 oligo = 0,3
 OPCs= 16
 Microglia = 11
 Endothelial = 18,20
 overlapping = 4
 novel = 1,2,6,8,15,16,22,23 - all likely neurons - all likely neurons


Assigning cell type identity to clusters: 

```{r}
Batch4_MTG <- RenameIdents(Batch4_MTG, `0` = "Oligodendrocytes", `1` = "Glu_Neurons", `2` = "Oligodendrocytes",
                      `3` = "Glu_Neurons", `4` = "Astrocytes/OPCs", `5` = "Novel Cluster 5",
                      `6` = "GABA Neurons", `7` = "GABA Neurons", `8` = "Microglia",`9` = "OPCs",
                      `10` = "Glu_Neurons", `11` = "Novel Cluster 11",`12` = "Novel Cluster 12",
                      `13` = "Novel Cluster 13",`14` = "Novel Cluster 14",
                      `15` = "Endothelial", `16`="GABA Neurons", `17`="Glu_Neurons", `18`="Astrocytes")
```

```{R}
#saveRDS(AllMB,"AllMB_Assigned.rds")
#AllMB=readRDS("AllMB.rds")
```

```{R}

#AllMB <- readRDS("Files/AllMB_Assigned.rds")

```



Now let's plot cells with the assigned celltypes: 
```{r}
DimPlot(Batch4_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2)

UMAPclusters <- DimPlot(Batch4_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Files/UMAPclusters_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

```{r}
DimPlot(Batch4_MTG, label = TRUE, repel = TRUE, pt.size = 1, split.by = "case", label.size = 2,
        ncol = 1) + NoLegend()
```


```{r}
DimPlot(Batch4_MTG, label = TRUE, repel = TRUE, pt.size = 1,reduction = 'umap')
```




