---
title: "ChooseR_Test"
output: html_document
---

```{R}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
library(glmpca)
library(SeuratWrappers)
```


Loading in the single cell data

```{r}
Batch7.data <- Read10X(data.dir = "Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
```


checking dimensions to check all samples have the same set of genes

```{r}

dim(Batch7.data)

```


```{r}
Batch7_MTG <- CreateSeuratObject(counts = cbind(Batch7.data),
                            project = "Batch7_MTG",
                            min.cells = 3)
```


```{R}
samples <- read.csv(file.path("Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)

cellcodes <- as.data.frame(Batch7_MTG@assays$RNA@data@Dimnames[[2]])
colnames(cellcodes) <- "barcodes"
rownames(cellcodes) <- cellcodes$barcodes

cellcodes$libcodes <- as.factor(gsub(pattern=".+-", replacement="", cellcodes$barcodes))
cellcodes$samples <- as.vector(samples$library_id[cellcodes$libcodes])

Batch7_MTG@meta.data$sample_ID <- cellcodes$samples

unique(Batch7_MTG@meta.data$sample_ID)

```


```{R}
samples$case <- c("HC","PD","HC")

cellcodes$case <- as.vector(samples$case[cellcodes$libcodes])

Batch7_MTG@meta.data$case <- cellcodes$case

```


```{r}
Batch7_MTG[["percent.mt"]] <- PercentageFeatureSet(Batch7_MTG, pattern = "^MT-")

VlnPlot(Batch7_MTG, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

```{R}
library(stats)
nfeature_RNA <- Batch7_MTG@meta.data$nFeature_RNA
mean(nfeature_RNA)
MAD <- mad(nfeature_RNA, center = median(nfeature_RNA))
threeMAD <- (MAD*3)+median(Batch7_MTG@meta.data$nFeature_RNA)

```


Filtering low quality cells:
```{r}
Batch7_MTG <- subset(Batch7_MTG, subset = nFeature_RNA > 200 & nFeature_RNA < threeMAD & percent.mt < 5)
```

Now let's recheck the cell the counts for each group:
```{r}
table(Batch7_MTG$sample_ID)
```


Now let's recheck the cell the counts for each group:
```{r}
table(Batch7_MTG$sample_ID)
```

```{R}
table(Batch7_MTG$case)
```


Log Normalizing data: 
```{r}
Batch7_MTG <- NormalizeData(Batch7_MTG, normalization.method = "LogNormalize", scale.factor = 10000)
```


Finding and plotting 2000 most variable features

```{R}
Batch7_MTG <- FindVariableFeatures(Batch7_MTG, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(Batch7_MTG), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(Batch7_MTG)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
```

```{R}
plot1
```

```{R}
plot2
```

Run the standard workflow for visualization and clustering :

save list of all genes
```{r}
all.genes <- rownames(Batch7_MTG)
```

center and scale data
```{r}
Batch7_MTG <- ScaleData(Batch7_MTG, features = all.genes, verbose = FALSE)
```


finding the top 30 principal components for cells
```{r}
Batch7_MTG <- RunGLMPCA(Batch7_MTG, features=Batch7_MTG@assays$RNA@var.features, L = 30)
```

see contribution of genes to construct each of these principal components.
```{r}
VizDimLoadings(Batch7_MTG, dims = 1:2, reduction = "glmpca")
```


plot cells in the first two principal components colored by case: 
```{r}
DimPlot(object = Batch7_MTG, reduction = "glmpca", pt.size = .1, group.by = "case")
```

Coordinate of cells in PC 1 characterized by case: 
```{r}
VlnPlot(object = Batch7_MTG, features = "PC_1", group.by = "case",  pt.size = .1)
```

Run Harmony
```{r}
Batch7_MTG <- RunHarmony(Batch7_MTG, group.by.vars = "case", reduction = "glmpca", plot_convergence = TRUE)

```

```{R}

source("~/bin/cluster.stability/R/pipeline.R")

```







