---
title: "Seurat Workflow and Cluster Assignment for Batch 7"
output: html_document
---

```{R}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
library(glmpca)
library(SeuratWrappers)
```



Loading in the single cell data

```{r}
Batch7.data <- Read10X(data.dir = "Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
```






checking dimensions to check all samples have the same set of genes

```{r}
dim(Batch7.data)


```


```{r}
Batch7_MTG <- CreateSeuratObject(counts = cbind(Batch7.data),
                            project = "Batch7_MTG",
                            min.cells = 3)
```


```{R}
samples <- read.csv(file.path("Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)

cellcodes <- as.data.frame(Batch7_MTG@assays$RNA@data@Dimnames[[2]])
colnames(cellcodes) <- "barcodes"
rownames(cellcodes) <- cellcodes$barcodes

cellcodes$libcodes <- as.factor(gsub(pattern=".+-", replacement="", cellcodes$barcodes))
cellcodes$samples <- as.vector(samples$library_id[cellcodes$libcodes])

Batch7_MTG@meta.data$sample_ID <- cellcodes$samples



```


```{R}

cellcodes$case <- as.vector(samples$case[cellcodes$libcodes])

Batch7_MTG@meta.data$case <- cellcodes$case

```




Now let's see the cell the counts for each group:
```{r}
table(Batch7_MTG$sample_ID)
```

```{R}
table(Batch7_MTG$case)
```


 Quality Checking : 

 Seurat allows you to easily explore QC metrics and filter cells based on any user-defined criteria.
 A few QC metrics commonly used by the community include : 
 The number of unique genes detected in each cell.
 Low-quality cells or empty droplets will often have very few genes
 Cell doublets or multiplets may exhibit an aberrantly high gene count
 Similarly, the total number of molecules detected within a cell (correlates strongly with unique genes)
 The percentage of reads that map to the mitochondrial genome
 Low-quality / dying cells often exhibit extensive mitochondrial contamination
 We calculate mitochondrial QC metrics with the PercentageFeatureSet() function, which calculates the percentage of counts originating from a set of features
 We use the set of all genes starting with MT- as a set of mitochondrial genes

```{r}
Batch7_MTG[["percent.mt"]] <- PercentageFeatureSet(Batch7_MTG, pattern = "^MT-")

VlnPlot(Batch7_MTG, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)


 average nfeature_RNA

```{R}
library(stats)
nfeature_RNA <- Batch7_MTG@meta.data$nFeature_RNA
mean(nfeature_RNA)
MAD <- mad(nfeature_RNA, center = median(nfeature_RNA))
threeMAD <- (MAD*3)+median(Batch7_MTG@meta.data$nFeature_RNA)

```


Filtering low quality cells:
```{r}
Batch7_MTG <- subset(Batch7_MTG, subset = nFeature_RNA > 200 & nFeature_RNA < threeMAD & percent.mt < 5)
```

Now let's recheck the cell the counts for each group:
```{r}
table(Batch7_MTG$sample_ID)
```

```{R}
table(Batch7_MTG$case)
```


Log Normalizing data: 
```{r}
Batch7_MTG <- NormalizeData(Batch7_MTG, normalization.method = "LogNormalize", scale.factor = 10000)
```


Finding and plotting 2000 most variable features

```{R}
Batch7_MTG <- FindVariableFeatures(Batch7_MTG, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(Batch7_MTG), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(Batch7_MTG)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
```

```{R}
plot1
```

```{R}
plot2
```

Run the standard workflow for visualization and clustering :

save list of all genes
```{r}
all.genes <- rownames(Batch7_MTG)
```

center and scale data
```{r}
Batch7_MTG <- ScaleData(Batch7_MTG, features = all.genes, verbose = FALSE)
```

Determining "Dimensionality" of the dataset





finding the top 30 principal components for cells
```{r}
Batch7_MTG <- RunPCA(Batch7_MTG, npcs = 30, verbose = FALSE)
```

see contribution of genes to construct each of these principal components.
```{r}
VizDimLoadings(Batch7_MTG, dims = 1:2, reduction = "pca")
```


plot cells in the first two principal components colored by case: 
```{r}
DimPlot(object = Batch7_MTG, reduction = "pca", pt.size = .1, group.by = "case")
```

Coordinate of cells in PC 1 characterized by case: 
```{r}
VlnPlot(object = Batch7_MTG, features = "PC_1", group.by = "case",  pt.size = .1)
```

Run Harmony
```{r}
Batch7_MTG <- RunHarmony(Batch7_MTG, group.by.vars = "case", plot_convergence = TRUE)
```


cells in harmony axis
```{r}
harmony_embeddings <- Embeddings(Batch7_MTG, 'harmony')
harmony_embeddings[1:5, 1:5]
```

cells in harmony axis
```{r}
DimPlot(object = Batch7_MTG, reduction = "harmony", pt.size = .1, group.by = "case")
```
cells in harmony 1 axis
```{r}
VlnPlot(object = Batch7_MTG, features = "harmony_1", group.by = "case",  pt.size = .1)
```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)
 2 dimensional reductions calculated: pca, harmony

Determing the dimensionality of the dataset

```{R}
#Batch7_MTG <- JackStraw(Batch7_MTG, num.replicate = 100)
#Batch7_MTG <- ScoreJackStraw(Batch7_MTG, dims = 1:12)
#JackStrawPlot(Batch7_MTG, dims = 1:20)



```

```{R}
ElbowPlot(Batch7_MTG)

```
10 looks like a suitable cutoff based on the elbow plot, but the JackStraw plot looks very strange

Finding Clusters of cells:
```{r}
Batch7_MTG <- FindNeighbors(Batch7_MTG, reduction = "harmony", dims = 1:20)
Batch7_MTG <- FindClusters(Batch7_MTG, resolution = 0.5, algorithm = 4)
```

run Umap based on top 10 harmony axis: 

```{r}
Batch7_MTG <- RunUMAP(Batch7_MTG, reduction = "harmony", dims = 1:20)
```

run tsne based on top 10 harmony axis: 

```{r}
#Batch7_MTG <- RunTSNE(Batch7_MTG, reduction = "harmony", dims = 1:17)
```

plot umap: 
```{r}
DimPlot(Batch7_MTG, reduction = "umap", label = TRUE,pt.size = 0.01)
```

```{r}
DimPlot(Batch7_MTG, reduction = "umap", group.by = "case",pt.size = 0.1)
```


```{r}
Batch7_MTG_Case_UMAP <- DimPlot(Batch7_MTG, reduction = "umap", label = TRUE, ncol = 1) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"),
              legend.position = "none")

ggsave(Batch7_MTG_Case_UMAP, filename = "Figures/Batch7_MTG_PCA_Leiden_UMAP.pdf", device = "pdf", width = 6, height = 6, units = "in")
```


