---
title: "Using PanglaoDB Markers and Method to Automate Cell Type Assignment"
output: html_document
---

```{R, message=FALSE}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
library(glmpca)
library(SeuratWrappers)
```



```{R}
Batch7_MTG=readRDS("Files/GLMPCA_Batch7_MTG_Unassigned.rds")
```


```{r}
DimPlot(Batch7_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5)
```
Try with both all markers and brain markers only

First with Brain Markers

Creating vector of median expression per gene for each cluster (common to both analyses)

```{R}

ClusterExpMed <- function(ClusterIdent, SeuObj) {
  IdentObj <- subset(SeuObj, idents = ClusterIdent)
  MedExp <- apply(IdentObj@assays$RNA@data, 1, median)
  return(MedExp)
}

ExpVectorPerCluster <- lapply(sort(as.numeric(unique(Batch7_MTG@active.ident))),FUN = ClusterExpMed, SeuObj = Batch7_MTG)

ExpVectorPerClusterDF <- as.data.frame(do.call(cbind, ExpVectorPerCluster))

colnames(ExpVectorPerClusterDF) <- sort(unique(Batch7_MTG@active.ident))

```

Creating gene weightings for the marker genes

```{R}
PanglaoDB <- read.delim("~/Documents/Projects/Misc. Files/PanglaoDB_markers_27_Mar_2020.tsv", stringsAsFactors = FALSE)

PanglaoDBBrain <- PanglaoDB[PanglaoDB$organ %in% "Brain",]

PanglaoDBBrain <- PanglaoDBBrain[!PanglaoDBBrain$species %in% "Mm",]

#PanglaoDBBrain <- PanglaoDBBrain[PanglaoDBBrain$canonical.marker %in% 1,]

1 + sqrt((length(unique(PanglaoDBBrain$cell.type)) - sum(PanglaoDBBrain$official.gene.symbol == "TH"))/(length(unique(PanglaoDBBrain$cell.type)) - 1))

AssignGeneWeights <- function(Gene) {
  Weight <- 1 + sqrt((length(unique(PanglaoDBBrain$cell.type)) - sum(PanglaoDBBrain$official.gene.symbol %in% Gene))/(length(unique(PanglaoDBBrain$cell.type)) - 1))
  return(Weight)
}

GeneWeights <- unlist(lapply(unique(PanglaoDBBrain$official.gene.symbol), AssignGeneWeights))

GeneWeightsDF <- as.data.frame(cbind(unique(PanglaoDBBrain$official.gene.symbol), GeneWeights))

colnames(GeneWeightsDF) <- c("Gene","Weight")

PanglaoDBBrain <- PanglaoDBBrain[PanglaoDBBrain$official.gene.symbol %in% rownames(Batch7_MTG@assays$RNA@counts),]

GeneWeightsDF <- GeneWeightsDF[GeneWeightsDF$Gene %in% PanglaoDBBrain$official.gene.symbol,]

PanglaoDBBrain$GeneWeights <- GeneWeightsDF$Weight[match(PanglaoDBBrain$official.gene.symbol,GeneWeightsDF$Gene)]

PanglaoDBBrain[PanglaoDBBrain$official.gene.symbol == "TH",]

#PanglaoDBBrain$ubiquitousness.index[PanglaoDBBrain$ubiquitousness.index == 0] <- NA

#PanglaoDBBrain <- PanglaoDBBrain %>% group_by(cell.type) %>% arrange(cell.type, ubiquitousness.index)
```


Calculating a CTA score for the clusters

```{R}

CellTypes <- unique(PanglaoDBBrain$cell.type)

PanglaoDBBrain$GeneWeights <- as.numeric(PanglaoDBBrain$GeneWeights)

CalculateCTA <- function(Cell, ClusterFrame, MarkerFrame) {
  CellMarkerFrame <- MarkerFrame[MarkerFrame$cell.type %in% Cell,]
  ClusterFrame$Genes <- rownames(ClusterFrame)
  CellClusterFrame <- as.data.frame(ClusterFrame[ClusterFrame$Genes %in% CellMarkerFrame$official.gene.symbol,])
  CellMarkerFrame <- CellMarkerFrame[order(match(CellMarkerFrame$official.gene.symbol,rownames(CellClusterFrame))),]
  CTAUnscaled <- CellClusterFrame[[1]]*CellMarkerFrame$GeneWeights
  CTAScore <- sum(CTAUnscaled/((length(CellMarkerFrame$official.gene.symbol))^1/3))
  return(CTAScore)
}

CellClusterAssignment=NULL
for (i in colnames(ExpVectorPerClusterDF)){
  ClusterColumn <- as.data.frame(ExpVectorPerClusterDF[[i]])
  rownames(ClusterColumn) <- rownames(ExpVectorPerClusterDF)
  colnames(ClusterColumn) <- "MedianExpression"
  CTAVector <- unlist(lapply(CellTypes, FUN = CalculateCTA, ClusterFrame = ClusterColumn, MarkerFrame = PanglaoDBBrain))
  names(CTAVector) <- CellTypes
  Assignment <- names(CTAVector[CTAVector == max(CTAVector)])
  CellClusterAssignment <- c(CellClusterAssignment,Assignment)
}

test <- as.data.frame(CellClusterAssignment)

```


```{R}

write.table(as.data.frame(CellClusterAssignment), file = "Files/CellClusterAssignment.tsv", quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t")



#test3 <- read.delim("Files/CellClusterAssignment.tsv")

```



```{R}
Batch7_MTG <- RenameIdents(Batch7_MTG, `1` = "Pyramidal", `2` = "Pyramidal", `3` = "Pyramidal",
                      `4` = "Neuroendocrine cells", `5` = "Pyramidal",
                      `6` = "Pyramidal", `7` = "Pyramidal", `8` = "Pyramidal",`9` = "Purkinje neurons",
                      `10` = "Pyramidal", `11` = "Glu Neurons",`12` = "Neuroendocrine cells",
                      `13` = "Radial glia cells",`14` = "Glu Neurons",
                      `15` = "Pyramidal", `16`="Neurons", `17`="Pyramidal", `18`="Glu Neurons", `19`="Oligodendrocyte progenitor cells",  `20`="Pyramidal", `21` = "Adrenergic neurons", `22` = "Neuroendocrine cells")


```


```{R}
DimPlot(Batch7_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2)

UMAPclusters <- DimPlot(Batch7_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Files/GMAPCA_UMAPclusters_PanglaoDBAssigned_scRNA_seq_Batch7.pdf", device = "pdf", width = 6, height = 4, units = "in")
```



Let's see how many unique cell types for the brain the database contains

```{R}
unique(PanglaoDBBrain$cell.type)

sum(is.na(PanglaoDBBrain$cell.type))
```



```{R}
VlnPlot(Batch7_MTG, features = c("NPFF","SLC18A2","SLC12A7","SYT1"),pt.size = 0,stack = TRUE, flip = TRUE)
```
```{r}
Batch7_MTG.markers <- FindAllMarkers(Batch7_MTG, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25, test.use = "MAST")
```

VGLUT1



```{R}

VlnPlot(Batch7_MTG, features = c("SLC17A7"),pt.size = 0)



```


###############################################################################################################


```{R, message=FALSE}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
library(glmpca)
library(SeuratWrappers)
```


```{R}
Batch7_MTG=readRDS("Files/GLMPCA_Batch7_MTG_Unassigned.rds")
```

Now using all the cell markers

```{r}
DimPlot(Batch7_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5)
```
Try with both all markers and  markers only

First with  Markers

Creating vector of median expression per gene for each cluster (common to both analyses)

```{R}

ClusterExpMed <- function(ClusterIdent, SeuObj) {
  IdentObj <- subset(SeuObj, idents = ClusterIdent)
  MedExp <- apply(IdentObj@assays$RNA@data, 1, median)
  return(MedExp)
}

ExpVectorPerCluster <- lapply(sort(as.numeric(unique(Batch7_MTG@active.ident))),FUN = ClusterExpMed, SeuObj = Batch7_MTG)

ExpVectorPerClusterDF <- as.data.frame(do.call(cbind, ExpVectorPerCluster))

colnames(ExpVectorPerClusterDF) <- sort(unique(Batch7_MTG@active.ident))

```

Creating gene weightings for the marker genes

```{R}
PanglaoDB <- read.delim("~/Documents/Projects/Misc. Files/PanglaoDB_markers_27_Mar_2020.tsv", stringsAsFactors = FALSE)

PanglaoDB <- PanglaoDB[!PanglaoDB$species %in% "Mm",]

#PanglaoDB <- PanglaoDB[PanglaoDB$canonical.marker %in% 1,]

1 + sqrt((length(unique(PanglaoDB$cell.type)) - sum(PanglaoDB$official.gene.symbol == "TH"))/(length(unique(PanglaoDB$cell.type)) - 1))

AssignGeneWeights <- function(Gene) {
  Weight <- 1 + sqrt((length(unique(PanglaoDB$cell.type)) - sum(PanglaoDB$official.gene.symbol %in% Gene))/(length(unique(PanglaoDB$cell.type)) - 1))
  return(Weight)
}

GeneWeights <- unlist(lapply(unique(PanglaoDB$official.gene.symbol), AssignGeneWeights))

GeneWeightsDF <- as.data.frame(cbind(unique(PanglaoDB$official.gene.symbol), GeneWeights))

colnames(GeneWeightsDF) <- c("Gene","Weight")

PanglaoDB <- PanglaoDB[PanglaoDB$official.gene.symbol %in% rownames(Batch7_MTG@assays$RNA@counts),]

GeneWeightsDF <- GeneWeightsDF[GeneWeightsDF$Gene %in% PanglaoDB$official.gene.symbol,]

PanglaoDB$GeneWeights <- GeneWeightsDF$Weight[match(PanglaoDB$official.gene.symbol,GeneWeightsDF$Gene)]

PanglaoDB[PanglaoDB$official.gene.symbol == "TH",]

#PanglaoDB$ubiquitousness.index[PanglaoDB$ubiquitousness.index == 0] <- NA

#PanglaoDB <- PanglaoDB %>% group_by(cell.type) %>% arrange(cell.type, ubiquitousness.index)
```


Calculating a CTA score for the clusters

```{R}

CellTypes <- unique(PanglaoDB$cell.type)

PanglaoDB$GeneWeights <- as.numeric(PanglaoDB$GeneWeights)

CalculateCTA <- function(Cell, ClusterFrame, MarkerFrame) {
  CellMarkerFrame <- MarkerFrame[MarkerFrame$cell.type %in% Cell,]
  ClusterFrame$Genes <- rownames(ClusterFrame)
  CellClusterFrame <- as.data.frame(ClusterFrame[ClusterFrame$Genes %in% CellMarkerFrame$official.gene.symbol,])
  CellMarkerFrame <- CellMarkerFrame[order(match(CellMarkerFrame$official.gene.symbol,rownames(CellClusterFrame))),]
  CTAUnscaled <- CellClusterFrame[[1]]*CellMarkerFrame$GeneWeights
  CTAScore <- sum(CTAUnscaled/((length(CellMarkerFrame$official.gene.symbol))^1/3))
  return(CTAScore)
}

CellClusterAssignment=NULL
for (i in colnames(ExpVectorPerClusterDF)){
  ClusterColumn <- as.data.frame(ExpVectorPerClusterDF[[i]])
  rownames(ClusterColumn) <- rownames(ExpVectorPerClusterDF)
  colnames(ClusterColumn) <- "MedianExpression"
  CTAVector <- unlist(lapply(CellTypes, FUN = CalculateCTA, ClusterFrame = ClusterColumn, MarkerFrame = PanglaoDB))
  names(CTAVector) <- CellTypes
  Assignment <- names(CTAVector[CTAVector == max(CTAVector)])
  CellClusterAssignment <- c(CellClusterAssignment,Assignment)
}

test <- as.data.frame(CellClusterAssignment)

```


```{R}

write.table(as.data.frame(CellClusterAssignment), file = "Files/CellClusterAssignment.tsv", quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t")



#test3 <- read.delim("Files/CellClusterAssignment.tsv")

```



```{R}
Batch7_MTG <- RenameIdents(Batch7_MTG, `1` = "Pyramidal", `2` = "Pyramidal", `3` = "Pyramidal",
                           `4` = "Neuroendocrine cells", `5` = "Pyramidal",
                           `6` = "Pyramidal", `7` = "Pyramidal", `8` = "Pyramidal",`9` = "Purkinje neurons",
                           `10` = "Pyramidal", `11` = "Glu Neurons",`12` = "Neuroendocrine cells",
                           `13` = "Radial glia cells",`14` = "Glu Neurons",
                           `15` = "Pyramidal", `16`="Neurons", `17`="Pyramidal", `18`="Glu Neurons", `19`="Oligodendrocyte progenitor cells",  `20`="Pyramidal", `21` = "Adrenergic neurons", `22` = "Neuroendocrine cells")


```


```{R}
DimPlot(Batch7_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2)

UMAPclusters <- DimPlot(Batch7_MTG, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5) + 
  theme(axis.text = element_text(size=8),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 8),
        title = element_text(size = 12),
        legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Files/GMAPCA_UMAPclusters_PanglaoDBAssignedALLCELLS_scRNA_seq_Batch7.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

