---
title: "Seurat Workflow and Cluster Assignment for pilot_2"
output: html_document
---

```{R}
library(Seurat)
library(cowplot)
library(ggplot2)
library(ggsci)
library(dplyr)
library(psych)
library(pheatmap)
library(harmony)
#library(clusterProfiler)
#library(org.Hs.eg.db)
library(DOSE)
library(GOSemSim)
library(enrichplot)
library(SeuratWrappers)
library(glmpca)
```



Load the BRI-318, BRI-319, BRI-320, BRI-321, B0085, H0321, H1009, H1118  single-cell data.

Loading in the single cell data

```{r}
Pilot_2.data <- Read10X(data.dir = "~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/Pilot_2/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices/filtered_feature_bc_matrix")
```






checking dimensions to check all samples have the same set of genes

```{r}
dim(Pilot_2.data)


```


```{r}
Pilot_2_MB <- CreateSeuratObject(counts = cbind(Pilot_2.data),
                            project = "Pilot_2_MB",
                            min.cells = 3)
```


```{R}
samples <- read.csv(file.path("~/Documents/Projects/PD5D_Repository/scRNA_and_scATAC-seq_Markdowns/Pilot_2/scRNA-seq/Files/cellranger_matrices/cellranger_aggr_matrices", "aggregation.csv"), stringsAsFactors=F)

cellcodes <- as.data.frame(Pilot_2_MB@assays$RNA@data@Dimnames[[2]])
colnames(cellcodes) <- "barcodes"
rownames(cellcodes) <- cellcodes$barcodes

cellcodes$libcodes <- as.factor(gsub(pattern=".+-", replacement="", cellcodes$barcodes))
cellcodes$samples <- as.vector(samples$library_id[cellcodes$libcodes])

Pilot_2_MB@meta.data$sample_ID <- cellcodes$samples



```


```{R}

cellcodes$case <- as.vector(samples$case[cellcodes$libcodes])

Pilot_2_MB@meta.data$case <- cellcodes$case

Pilot_2_MB@meta.data$region <- "Midbrain"

```





 Quality Checking : 

 Seurat allows you to easily explore QC metrics and filter cells based on any user-defined criteria.
 A few QC metrics commonly used by the community include : 
 The number of unique genes detected in each cell.
 Low-quality cells or empty droplets will often have very few genes
 Cell doublets or multiplets may exhibit an aberrantly high gene count
 Similarly, the total number of molecules detected within a cell (correlates strongly with unique genes)
 The percentage of reads that map to the mitochondrial genome
 Low-quality / dying cells often exhibit extensive mitochondrial contamination
 We calculate mitochondrial QC metrics with the PercentageFeatureSet() function, which calculates the percentage of counts originating from a set of features
 We use the set of all genes starting with MT- as a set of mitochondrial genes

```{r}
Pilot_2_MB[["percent.mt"]] <- PercentageFeatureSet(Pilot_2_MB, pattern = "^MT-")
VlnPlot(Pilot_2_MB, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)
 
 
```{R}
library(stats)
nfeature_RNA <- Pilot_2_MB@meta.data$nFeature_RNA
mean(nfeature_RNA)
MAD <- mad(nfeature_RNA, center = median(nfeature_RNA))
threeMAD <- (MAD*3)+median(Pilot_2_MB@meta.data$nFeature_RNA)

```

```{R}

dim(Pilot_2_MB)
```


Filtering low quality cells:
```{r}
Pilot_2_MB <- subset(Pilot_2_MB, subset = nFeature_RNA > 200 & nFeature_RNA < threeMAD | percent.mt < 5)
```


```{R}
dim(Pilot_2_MB)


```


Log Normalizing data: 
```{r}
Pilot_2_MB <- NormalizeData(Pilot_2_MB, normalization.method = "LogNormalize", scale.factor = 10000)
```


Finding and plotting 2000 most variable features

```{R}
Pilot_2_MB <- FindVariableFeatures(Pilot_2_MB, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(Pilot_2_MB), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(Pilot_2_MB)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1 + plot2
plot1
```

```{R}
plot2
```

Run the standard workflow for visualization and clustering :

save list of all genes
```{r}
all.genes <- rownames(Pilot_2_MB)
```

center and scale data
```{r}
Pilot_2_MB <- ScaleData(Pilot_2_MB, features = all.genes, verbose = FALSE)
```

finding the top 30 principal components for cells
```{r}
Pilot_2_MB <- RunGLMPCA(Pilot_2_MB, features=Pilot_2_MB@assays$RNA@var.features, L = 30)
```

see contribution of genes to construct each of these principal components.
```{r}
VizDimLoadings(Pilot_2_MB, dims = 1:2, reduction = "glmpca")
```


plot cells in the first two principal components colored by case: 
```{r}
DimPlot(object = Pilot_2_MB, reduction = "glmpca", pt.size = .1, group.by = "case")
```

Coordinate of cells in PC 1 characterized by case: 
```{r}
VlnPlot(object = Pilot_2_MB, features = "PC_1", group.by = "case",  pt.size = .1)
```

Run Harmony
```{r}
Pilot_2_MB <- RunHarmony(Pilot_2_MB, group.by.vars = c("sample_ID","case"), plot_convergence = TRUE, reduction = "glmpca", theta=c(1,1))
```


cells in harmony axis
```{r}
harmony_embeddings <- Embeddings(AllMB, 'harmony')
harmony_embeddings[1:5, 1:5]
```

cells in harmony axis
```{r}
DimPlot(object = Pilot_2_MB, reduction = "harmony", pt.size = .1, group.by = "case")
```
cells in harmony 1 axis
```{r}
VlnPlot(object = Pilot_2_MB, features = "harmony_1", group.by = "case",  pt.size = .1)
```


```{R}

ElbowPlot(Pilot_2_MB, reduction = "harmony")

```

 An object of class Seurat 
 25381 features across 6549 samples within 1 assay 
 Active assay: RNA (25381 features)
 2 dimensional reductions calculated: pca, harmony

Finding Clusters of cells:
```{r}
Pilot_2_MB <- FindNeighbors(Pilot_2_MB, reduction = "harmony", dims = 1:12)
Pilot_2_MB <- FindClusters(Pilot_2_MB, resolution = 0.5, algorithm = 4)
```

run Umap based on top 20 harmony axis: 

```{r}
Pilot_2_MB <- RunUMAP(Pilot_2_MB, reduction = "harmony", dims = 1:12)
```

run tsne based on top 20 harmony axis: 

```{r}
#AllMB <- RunTSNE(AllMB, reduction = "harmony", dims = 1:15)
```

plot umap: 
```{r}
DimPlot(Pilot_2_MB, reduction = "umap", label = TRUE,pt.size = 0.01)
```

```{r}
DimPlot(Pilot_2_MB, reduction = "umap", group.by = "case",pt.size = 0.1)
```

```{r}
DimPlot(AllMB, reduction = "umap", group.by = "experiment",pt.size = 0.1)
```

TSNE Plot cells colored by clusters and grouped by case. 
```{r}
DimPlot(Pilot_2_MB, reduction = "umap", split.by = "case", label = TRUE, ncol = 1)
```

Figures_Pilot_2

Now let's plot cells with the assigned celltypes: 
```{r}
DimPlot(Pilot_2_MB, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2)

UMAPclusters <- DimPlot(Pilot_2_MB, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Figures_Pilot_2/Unassigned_UMAPclusters_scRNA_seq_Pilot_2.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
UMAPclusters <- DimPlot(Pilot_2_MB, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5, split.by = "case") + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Figures_Pilot_2/Unassigned_Split_UMAPclusters_scRNA_seq_Pilot_2.pdf", device = "pdf", width = 12, height = 4, units = "in")
```


Find markers for every cluster compared to all remaining cells, report only the positive ones
```{r}
AllMB.markers <- FindAllMarkers(AllMB, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
```


Save single-cell elements. 
```{r}
#saveRDS(AllMB,"AllMB.rds")
```

```{r}
#AllMB=readRDS("AllMB.rds")
```

```{r}
#saveRDS(AllMB.markers,"AllMB.markers.rds")
```

```{r}
#AllMB.markers=readRDS("AllMB.markers.rds")
#write.csv(AllMB.markers,"AllMB_markers.csv")
```

```{r}
unique(AllMB.markers$cluster)
```

Top marker genes for each clusters: 
```{r}
AllMB.markers %>% group_by(cluster) %>% top_n(n = 2, wt = avg_logFC)
write.table(AllMB.markers, file = "AllMarkers.txt", col.names = TRUE, sep = "\t", quote = FALSE)
top10Markers <- AllMB.markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_logFC)
write.table(top10Markers, file = "top10Markers.txt", col.names = TRUE, sep = "\t", quote = FALSE)
```

Heatmap for some marker genes: 
```{r}
features <- unique(top10Markers$gene)
DoHeatmap(AllMB, features = features, size = 2, draw.lines = FALSE, angle = 45,
          hjust = 0.2) + theme(axis.text.y = element_text(size = 5))
```

```{r}
VlnPlot(AllMB, features = c("SLC32A1", "GAD1", "GAD2", "SLC17A6", "LPL", "OTX2", "ADCYAP1", "GRP", "VIP"),
        ncol = 1)
VlnPlot(AllMB, features = "LINC01608",
        ncol = 1)
```
Plot these genes in the cluster plot:
```{r}
FeaturePlot(AllMB, features = c("ENO2", "RBFOX3","SLC17A6", "SLC17A7","AQP4", "GFAP"))
```

```{r}
FeaturePlot(AllMB, features = c("SLC17A6", "SLC17A7"))
```

```{r}
saveRDS(Pilot_2_MB,"Pilot_2_MB_Unassigned.rds")
```

 Neuron  = ENO2, RBFOX3
 Glutamatergic neurons = SLC17A6, SLC17A7
 GABAergic neurons = SLC32A1, GAD1, GAD2
 Dopaminergic neurons = TH, SLC6A3, SCL18A2
 Astrocytes  = AQP4, GFAP
 Oligodendrocytes  =  PLP1, MBP
 OPCs  =  VCAN, BCAN,
 Microglia = CX3CR1, P2RY12
 Endothelial cells = FLT1, CLDN5
 

 Glu_Neurons=10
 GABA_Neurons = 5
 Glu_GABA Neurons = 17
 Dop_Neurons subgroup 1 = 12
 Dop_Neurons subgroup 2 = 18
 Astrocytes = 3,8
 oligo = 0,1,2,7
 OPCs=4
 Microglia = 6
 Endothelial= 9,11,15
 novel = 13, 14, 16
 
 #########################################################
 
```{R}
Pilot_2_MB=readRDS("Files/Pilot_2_MB_Unassigned.rds")
```


```{R}
UMAPclusters <- DimPlot(Pilot_2_MB, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Figures/Unassigned_UMAPclusters_scRNA_seq_Pilot_2.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


Testing T-cell/immune cell markers




```{r}
VlnPlot(Pilot_2_MB, features = c("CD96"),pt.size = 0)
```
NK Cell Markers

```{r}
VlnPlot(Pilot_2_MB, features = c("IL7R"),pt.size = 0)
```


CD16

```{r}
VlnPlot(Pilot_2_MB, features = c("FCGR3A"),pt.size = 0)
```

CD56

```{r}
VlnPlot(Pilot_2_MB, features = c("NCAM1"),pt.size = 0)
```

CD94


```{r}
VlnPlot(Pilot_2_MB, features = c("KLRD1"),pt.size = 0)
```
NKG2A

```{r}
VlnPlot(Pilot_2_MB, features = c("KLRC1"),pt.size = 0)
```
```{r}
VlnPlot(Pilot_2_MB, features = c("CD244"),pt.size = 0)
```

resting T cell marker?

```{r}
VlnPlot(Pilot_2_MB, features = c("CD226"),pt.size = 0)
```

```{r}
VlnPlot(Pilot_2_MB, features = c("CD8A"),pt.size = 0)
```
```{r}
#VlnPlot(AllMB, features = c("1C7"),pt.size = 0)
```

```{r}
TKillerCellMarkerVlnPlot <- VlnPlot(Pilot_2_MB, features = c("CD8A","CD226","CD244","CD96","IL7R","KLRD1","NCAM1","FCGR3A","KLRC1"),pt.size = 0, ncol = 1) 

ggsave(TKillerCellMarkerVlnPlot,filename = "TKillerCellMarkerVlnPlot.pdf", width = 20, height = 20)            


```


##################################################################

T lymphocyte markers

```{r}
VlnPlot(AllMB, features = c("CD69"),pt.size = 0)
```



```{r}
VlnPlot(AllMB, features = c("TFRC"),pt.size = 0)
```



```{r}
VlnPlot(AllMB, features = c("IL2RA"),pt.size = 0)
```



```{r}
VlnPlot(AllMB, features = c("CTLA4"),pt.size = 0)
```



```{r}
VlnPlot(AllMB, features = c("FOXP3"),pt.size = 0)
```




###################################################################

Find cell-types by plotting marker genes.
```{r}
VlnPlot(Pilot_2_MB, features = c("ENO2"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("RBFOX3"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("SLC17A6"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("SLC17A7"),pt.size = 0)
```

GLU 9,10,19

```{R}
VlnPlot(Pilot_2_MB, features = c("SLC32A1"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("GAD1"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("GAD2"),pt.size = 0)
```
GABA - 5,6,10,16,18


```{R}
VlnPlot(Pilot_2_MB, features = c("TH"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("SLC6A3"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("SLC18A2"),pt.size = 0)
```

DA Neurons - 12


```{R}
VlnPlot(Pilot_2_MB, features = c("AQP4"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("GFAP"),pt.size = 0)
```


```{R}
VlnPlot(Pilot_2_MB, features = c("ALDH1L1"),pt.size = 0)
```


Astrocyte - 2


```{R}
VlnPlot(Pilot_2_MB, features = c("PLP1"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("MBP"),pt.size = 0)
```

oligo 1,3,15


```{R}
VlnPlot(Pilot_2_MB, features = c("VCAN"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("BCAN"),pt.size = 0)
```
OPCs - 6


```{R}
VlnPlot(Pilot_2_MB, features = c("CX3CR1"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("P2RY12"),pt.size = 0)
```

Microglia - 4


```{R}
VlnPlot(Pilot_2_MB, features = c("FLT1"),pt.size = 0)
```
```{R}
VlnPlot(Pilot_2_MB, features = c("CLDN5"),pt.size = 0)
```

Endothelial - 7,8,17


```{R}
VlnPlot(Pilot_2_MB, features = c("RELN"),pt.size = 0)
```


```{R}
VlnPlot(Pilot_2_MB, features = c("CALB2"),pt.size = 0)
```


```{R}
VlnPlot(Pilot_2_MB, features = c("CNR1"),pt.size = 1)
```

```{R}
VlnPlot(Pilot_2_MB, features = c("PAFAH1B1"),pt.size = 1)
```



```{r}
VlnPlot(AllMB, features = c("ENO2",
                            "TH",
                            "SLC6A3",
                            "SLC18A2",
                            "SLC17A6",
                            "SLC17A7",
                            "SLC32A1",
                            "GAD1",
                            "GAD2",
                            "AQP4",
                            "GFAP",
                            "PLP1",
                            "OLIG1",
                            "VCAN",
                            "CX3CR1",
                            "P2RY12",
                            "FLT1"),
        pt.size =0,ncol = 1)

#ggsave(thisplot, filename = "testplot", device = "pdf")
```

Find mean values of these genes across clusters.
```{r}
AverageExpression(AllMB, features = c("ENO2",
                                      "TH",
                                      "SLC6A3",
                                      "SLC18A2",
                                      "SLC17A6",
                                      "SLC17A7",
                                      "SLC32A1",
                                      "GAD1",
                                      "GAD2",
                                      "AQP4",
                                      "GFAP",
                                      "PLP1",
                                      "OLIG1",
                                      "VCAN",
                                      "CX3CR1",
                                      "P2RY12",
                                      "FLT1"),use.counts=TRUE)
```
Other form of ploting genes across clusters:
```{r}
RidgePlot(AllMB, features=c("ENO2"))
RidgePlot(AllMB, features=c("TH"))
RidgePlot(AllMB, features=c("SLC6A3"))
RidgePlot(AllMB, features=c("SLC18A2"))
RidgePlot(AllMB, features=c("SLC17A6"))
RidgePlot(AllMB, features=c("GAD2"))
```

 
  Neuron  = ENO2, RBFOX3
 Glutamatergic neurons = SLC17A6, SLC17A7
 GABAergic neurons = SLC32A1, GAD1, GAD2
 Dopaminergic neurons = TH, SLC6A3, SCL18A2
 Astrocytes  = AQP4, GFAP
 Oligodendrocytes  =  PLP1, MBP
 OPCs  =  VCAN, BCAN,
 Microglia = CX3CR1, P2RY12
 Endothelial cells = FLT1, CLDN5
 
 
 Glu_Neurons=10
 GABA_Neurons = 5
 Glu_GABA Neurons = 17
 Dop_Neurons subgroup 1 = 12
 Dop_Neurons subgroup 2 = 18
 Astrocytes = 3,8
 oligo = 0,1,2,7
 OPCs=4
 Microglia = 6
 Endothelial= 9,11, 15
 novel = 13, 14, 16

GLU 9,10,19
GABA - 5,6,10,16,18
DA Neurons - 12
Astrocyte - 2
oligo 1,3,15
OPCs - 6
Microglia - 4
Endothelial - 7,8,17
novel=11,14

Assigning cell type identity to clusters: 

```{r}
Pilot_2_MB <- RenameIdents(Pilot_2_MB, `1` = "Oligodendrocytes", `2` = "Astrocytes",
                      `3` = "Oligodendrocytes", `4` = "Microglia", `5` = "GABA neurons",
                      `6` = "GABA neurons", `7` = "Endothelial", `8` = "GABA neurons",`9` = "GLU neurons",
                      `10` = "GLU_GABA Neurons", `11` = "Dopaminergic Neurons group 1",`12` = "Dopaminergic Neurons group 2",
                      `13` = "CD8+ T Cells",`14` = "Cajal-Retzius Cells?",
                      `15` = "Oligodendrocytes", `16`="GABA neurons", `17`="Endothelial", `18`="GABA neurons", `19`="GLU neurons")
```

```{r}
AllMB_group_assigned <- RenameIdents(AllMB, `0` = "Oligodendrocytes", `1` = "Oligodendrocytes", `2` = "Oligodendrocytes", `3` = "Astrocytes 1", `4` = "Oligodendrocytes", `5` = "GLU/GABA Neurons",`6` = "Microglia", `7` = "Oligodendrocytes", `8` = "Astrocytes 2",`9` = "Endothelial cells",`10` = "GLU/GABA Neurons", `11` = "Endothelial cells",`12` = "Dopaminergic Neurons",`13` = "CD8+ T Cells",`14` = "Novel Cluster 14",`15` = "Endothelial cells", `16`="Novel Cluster 16", `17`="GLU/GABA Neurons", `18`="Dopaminergic Neurons")
```


```{R}
saveRDS(AllMB_group_assigned,"AllMB_Group_Assigned.rds")
#AllMB=readRDS("AllMB.rds")
```


```{R}
#saveRDS(AllMB,"AllMB_Assigned.rds")
#AllMB=readRDS("AllMB.rds")
```




```{R}

AllMB <- readRDS("Files/AllMB_Assigned.rds")

```

what are dopaminergic neurons DA1 and DA2?


Now let's plot cells with the assigned celltypes: 
```{r}
DimPlot(Pilot_2_MB, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2)

UMAPclusters <- DimPlot(Pilot_2_MB, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5) + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Figures/UMAPclusters_scRNA_seq_Pilot_2.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
UMAPclusters <- DimPlot(Pilot_2_MB, label = TRUE, repel = TRUE, pt.size = 0, label.size = 2.5, split.by = "case") + 
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(UMAPclusters, filename = "Figures_Pilot_2/Split_UMAPclusters_scRNA_seq_Pilot_2.pdf", device = "pdf", width = 12, height = 4, units = "in")
```


```{r}
DimPlot(AllMB, label = TRUE, repel = TRUE, pt.size = 1, split.by = "case", label.size = 2,
        ncol = 1) + NoLegend()
```


```{r}
DimPlot(AllMB, label = TRUE, repel = TRUE, pt.size = 1,reduction = 'umap')
```




```{R}
VlnPlot(AllMB, features = c("RIMS1"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

RIMS1Vln <- VlnPlot(AllMB, features = c("RIMS1"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(RIMS1Vln, filename = "RIMS1_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")


```

```{R}
VlnPlot(AllMB, features = c("RIMS2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

RIMS2Vln <- VlnPlot(AllMB, features = c("RIMS2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


ggsave(RIMS2Vln, filename = "RIMS2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```





```{R}
VlnPlot(AllMB, features = c("BIN1"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

BIN1Vln <- VlnPlot(AllMB, features = c("BIN1"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(BIN1Vln, filename = "BIN1_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
VlnPlot(AllMB, features = c("BIN2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

BIN2Vln <- VlnPlot(AllMB, features = c("BIN2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(BIN2Vln, filename = "BIN2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```





```{R}
VlnPlot(AllMB, features = c("BIN3"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

BIN3Vln <- VlnPlot(AllMB, features = c("BIN3"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(BIN3Vln, filename = "BIN3_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

```{R}
VlnPlot(AllMB, features = c("TH"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

THVln <- VlnPlot(AllMB, features = c("TH"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(THVln, filename = "TH_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```
SLC6A3, 

```{R}
VlnPlot(AllMB, features = c("SLC6A3"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

SLC6A3Vln <- VlnPlot(AllMB, features = c("SLC6A3"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(SLC6A3Vln, filename = "SLC6A3_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
VlnPlot(AllMB, features = c("SLC18A2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

SLC18A2Vln <- VlnPlot(AllMB, features = c("SLC18A2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(SLC18A2Vln, filename = "SLC18A2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

```{R}
VlnPlot(AllMB, features = c("DGKQ"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

#SLC18A2Vln <- VlnPlot(AllMB, features = c("DGKQ"),pt.size = 0) +
#        theme(axis.text = element_text(size=8),
#              axis.title = element_text(size = 12),
#              legend.text = element_text(size = 8),
#              title = element_text(size = 12),
#              legend.key.size = unit(0.4,"cm"))

#ggsave(SLC18A2Vln, filename = "SLC18A2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```



```{R}
VlnPlot(AllMB, features = c("SH3GL2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

SH3GL2Vln <- VlnPlot(AllMB, features = c("SH3GL2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))

ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


##################################################################

Differentiating betweening dopaminergic neuron subtypes

#################################################################

```{r}
VlnPlot(AllMB, features = c("SOX6"),pt.size = 0)
```


```{r}
VlnPlot(AllMB, features = c("NDNF"),pt.size = 0)
```

```{r}
VlnPlot(AllMB, features = c("ALDH1A1"),pt.size = 0)
```


```{r}
VlnPlot(AllMB, features = c("CALB1"),pt.size = 0)
```
GIRK2

```{r}
VlnPlot(AllMB, features = c("KCNJ6"),pt.size = 0)
```



```{r}
#VlnPlot(AllMB, features = c("KCNJ3"),pt.size = 0)
```


```{r}
VlnPlot(AllMB, features = c("OTX2"),pt.size = 0)
```



```{r}
VlnPlot(AllMB, features = c("ADCYAP1"),pt.size = 0)
```





```{r}
VlnPlot(AllMB, features = c("VIP"),pt.size = 0)
```


vglut

```{r}
VlnPlot(AllMB, features = c("SLC17A6"),pt.size = 0)
```


vgat

```{r}
VlnPlot(AllMB, features = c("SLC32A1"),pt.size = 0)
```




```{r}
VlnPlot(AllMB, features = c("CCK"),pt.size = 0)
```

```{r}
DANeuronSubtypesCellMarkerVlnPlot <- VlnPlot(AllMB, features = c("ALDH1A1","SOX6","CALB1","KCNJ6","SLC17A6"),pt.size = 0, ncol = 1) 

ggsave(DANeuronSubtypesCellMarkerVlnPlot,filename = "DANeuronSubtypesCellMarkerVlnPlot.pdf", width = 20, height = 20)            


```



#####################################################################


Markers DE between SN and VA DA neurons according to Aguila et al. paper

```{R}
VlnPlot(AllMB, features = c("ZCCHC12"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


cluster 12: CALB1~+, SOX6+, GIRK2+ (more than 18)

cluster 18: Vglut+, GIRK2+ (although less than 12), ALDH1A1+ 


```{R}
VlnPlot(AllMB, features = c("CDH13"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

```{R}
VlnPlot(AllMB, features = c("SERPINE2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

```{R}
VlnPlot(AllMB, features = c("SLIT1"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
VlnPlot(AllMB, features = c("GSG1L"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```




```{R}
VlnPlot(AllMB, features = c("SEZ6"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```




```{R}
VlnPlot(AllMB, features = c("ATP2A3"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```



```{R}
VlnPlot(AllMB, features = c("SLC17A6"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```



```{R}
VlnPlot(AllMB, features = c("RGS16"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```




```{R}
VlnPlot(AllMB, features = c("PCP4"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```
```{R}
VlnPlot(AllMB, features = c("CADM1"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```

```{R}
VlnPlot(AllMB, features = c("TIMP2"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
VlnPlot(AllMB, features = c("NECAB1"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
VlnPlot(AllMB, features = c("PCP4"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```


```{R}
VlnPlot(AllMB, features = c("PCP4"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```



```{R}
VlnPlot(AllMB, features = c("PCP4"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```



```{R}
VlnPlot(AllMB, features = c("PCP4"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```



```{R}
VlnPlot(AllMB, features = c("PCP4"),pt.size = 0) +
        theme(axis.text = element_text(size=8),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 8),
              title = element_text(size = 12),
              legend.key.size = unit(0.4,"cm"))


#ggsave(SH3GL2Vln, filename = "SH3GL2_Vln_scRNA_seq_Batch4.pdf", device = "pdf", width = 6, height = 4, units = "in")
```




